---
output: github_document
---

# ggsignif: Significance Brackets for 'ggplot2' <a href='https://github.com/const-ae/ggsignif'><img src='man/figures/logo.svg' align="right" height="209" /></a>

[![CRAN_Status_Badge](https://www.r-pkg.org/badges/version/ggsignif)](https://cran.r-project.org/package=ggsignif)
[![R build status](https://github.com/const-ae/ggsignif/workflows/R-CMD-check/badge.svg)](https://github.com/const-ae/ggsignif)
[![Total downloads badge](https://cranlogs.r-pkg.org/badges/grand-total/ggsignif?color=blue)](https://CRAN.R-project.org/package=ggsignif)
[![Codecov test coverage](https://codecov.io/gh/const-ae/ggsignif/branch/master/graph/badge.svg)](https://codecov.io/gh/const-ae/ggsignif?branch=master)
[![lifecycle](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://lifecycle.r-lib.org/articles/stages.html)

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  dpi = 300,
  out.width = "100%",
  fig.path = "man/figures/README-",
  message = FALSE,
  warning = FALSE
)
```

## Introduction

This package provides an easy way to indicate if two groups are significantly
different. Commonly this is shown by a bar on top connecting the groups of
interest which itself is annotated with the level of significance (NS, \*, \*\*,
\*\*\*). The package provides a single layer (`geom_signif`) that takes the
groups for comparison and the test (t.test, wilcox etc.) and adds the annotation
to the plot.

## Citation

If you wish to cite this package in a publication, you can run the following
command in your R console:

```{r citation}
citation("ggsignif")
```

## Example

You can first install this package from `CRAN`:

```{r eval=FALSE}
install.packages("ggsignif")
```

Or get the latest development version:

```{r eval=FALSE}
install.packages("remotes")
remotes::install_github("const-ae/ggsignif")
```

Plot significance

```{r simpe_comparison}
library(ggplot2)
library(ggsignif)

p1 <- ggplot(mpg, aes(class, hwy)) +
  geom_boxplot() +
  geom_signif(
    comparisons = list(c("compact", "midsize"), c("minivan", "suv")),
    map_signif_level = TRUE, textsize = 6
  ) +
  ylim(NA, 48)
p1
```

Control the direction (either `x` or `y`) via `orientation` 

```{r orientation_argument}
p2 <- ggplot(
  data = mpg,
  mapping = aes(
    x = hwy,
    y = class
  )
) +
  geom_boxplot(
    orientation = "y"
  ) +
  geom_signif(
    comparisons = list(
      c("compact", "midsize"),
      c("minivan", "suv")
    ),
    map_signif_level = TRUE,
    textsize = 6,
    margin_top = 0.08,
    step_increase = 0.05,
    tip_length = 0.01,
    orientation = "y"
  )
p2
```

Compatible with coord_flip

```{r coord_flip}
p1 + coord_flip()
``` 

Setting the precise location

This is important if you use `position="dodge"`, because in that case I cannot
calculate the correct position of the bars automatically.

```{r dodge_comparison}
# Calculate annotation
anno <- t.test(
  iris[iris$Petal.Width > 1 & iris$Species == "versicolor", "Sepal.Width"],
  iris[iris$Species == "virginica", "Sepal.Width"]
)$p.value

# Make plot with custom x and y position of the bracket
ggplot(iris, aes(x = Species, y = Sepal.Width, fill = Petal.Width > 1)) +
  geom_boxplot(position = "dodge") +
  geom_signif(
    annotation = formatC(anno, digits = 1),
    y_position = 4.05, xmin = 2.2, xmax = 3,
    tip_length = c(0.2, 0.04)
  )
```

Advanced Example

Sometimes one needs to have a very fine tuned ability to set the location of the
the significance bars in combination with `facet_wrap` or `facet_grid`. In those
cases it you can set the flag `manual=TRUE` and provide the annotations as a
data.frame:

```{r faceted_comparison}
annotation_df <- data.frame(
  color = c("E", "H"),
  start = c("Good", "Fair"),
  end = c("Very Good", "Good"),
  y = c(3.6, 4.7),
  label = c("Comp. 1", "Comp. 2")
)

annotation_df

ggplot(diamonds, aes(x = cut, y = carat)) +
  geom_boxplot() +
  geom_signif(
    data = annotation_df,
    aes(xmin = start, xmax = end, annotations = label, y_position = y),
    textsize = 3, vjust = -0.2,
    manual = TRUE
  ) +
  facet_wrap(~color) +
  ylim(NA, 5.3)
```

You can ignore the warning about the missing aesthetics.

For further details, see:
<https://const-ae.github.io/ggsignif/articles/intro.html>

## Maintenance

This package is provided as is and we currently don't have any plans and the
capacity to add any new features to it. If there is nonetheless a feature which
you would like to see in the package, you are always welcome to submit pull
request, which we will try to address as soon as possible.

## Code of Conduct
  
Please note that the `ggsignif` project is released with a [Contributor Code of Conduct](https://const-ae.github.io/ggsignif/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
