---
output: github_document
---

# ggsignif <a href='https://github.com/const-ae/ggsignif'><img src='man/figures/logo.svg' align="right" height="209" /></a>

[![CRAN_Status_Badge](https://www.r-pkg.org/badges/version/ggsignif)](https://cran.r-project.org/package=ggsignif)
[![R build status](https://github.com/const-ae/ggsignif/workflows/R-CMD-check/badge.svg)](https://github.com/const-ae/ggsignif)
[![Downloads](https://cranlogs.r-pkg.org/badges/last-month/ggsignif?color=brightgreen)](https://cran.r-project.org/package=ggsignif)
[![Codecov test coverage](https://codecov.io/gh/const-ae/ggsignif/branch/master/graph/badge.svg)](https://codecov.io/gh/const-ae/ggsignif?branch=master)

Easily add significance bars to your ggplots

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  message = FALSE,
  warning = FALSE
)
```

## Description

This package provides an easy way to indicate if two groups are significantly
different. Commonly this is shown by a bar on top connecting the groups of
interest which itself is annotated with the level of significance (NS, \*, \*\*,
\*\*\*). The package provides a single layer (geom_signif) that takes the groups
for comparison and the test (t.test, wilcox etc.) and adds the annotation to the
plot.

## Example

Install package

```{r eval=FALSE}
install.packages("ggsignif")

# Or for the latest development version
remotes::install_github("const-ae/ggsignif")
```

Plot significance

```{r simpe_comparison}
library(ggplot2)
library(ggsignif)

ggplot(mpg, aes(class, hwy)) +
  geom_boxplot() +
  geom_signif(
    comparisons = list(c("compact", "midsize"), c("minivan", "suv")),
    map_signif_level = TRUE, textsize = 6
  ) +
  ylim(NA, 48)
```

Setting the precise location

This is important if you use `position="dodge"`, because in that case I cannot
calculate the correct position of the bars automatically.

```{r dodge_comparison}
# Calculate annotation
anno <- t.test(
  iris[iris$Petal.Width > 1 & iris$Species == "versicolor", "Sepal.Width"],
  iris[iris$Species == "virginica", "Sepal.Width"]
)$p.value

# Make plot with custom x and y position of the bracket
ggplot(iris, aes(x = Species, y = Sepal.Width, fill = Petal.Width > 1)) +
  geom_boxplot(position = "dodge") +
  geom_signif(
    annotation = formatC(anno, digits = 1),
    y_position = 4.05, xmin = 2.2, xmax = 3,
    tip_length = c(0.2, 0.04)
  )
```


Advanced Example

Sometimes one needs to have a very fine tuned ability to set the location of the
the significance bars in combination with `facet_wrap` or `facet_grid`. In those
cases it you can set the flag `manual=TRUE` and provide the annotations as a
data.frame:

```{r faceted_comparison}
annotation_df <- data.frame(
  color = c("E", "H"),
  start = c("Good", "Fair"),
  end = c("Very Good", "Good"),
  y = c(3.6, 4.7),
  label = c("Comp. 1", "Comp. 2")
)

annotation_df

ggplot(diamonds, aes(x = cut, y = carat)) +
  geom_boxplot() +
  geom_signif(
    data = annotation_df,
    aes(xmin = start, xmax = end, annotations = label, y_position = y),
    textsize = 3, vjust = -0.2,
    manual = TRUE
  ) +
  facet_wrap(~color) +
  ylim(NA, 5.3)
```

You can ignore the warning about the missing aesthetics.

For further details go the [CRAN page](https://CRAN.R-project.org/package=ggsignif) and check the examples in the [vignette](https://CRAN.R-project.org/package=ggsignif/vignettes/intro.html).

## Maintenance

This package is provided as is and I currently don't have any plans and the
capacity to add any new features to it. If there is nonetheless a feature which
you would like to see in the package, you are always welcome to submit pull
request, which I will try to address as soon as possible.

## Code of Conduct
  
  Please note that the ggsignif project is released with a [Contributor Code of Conduct](https://const-ae.github.io/ggsignif/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
