---
title: "ggsignif intro"
author: "Constantin Ahlmann-Eltze"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{ggsignif intro}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This package provides an extension for the popular ggplot2 package.

Often people are looking for a way to quickly annotate if the difference between 2 groups in a plot is
significantly different 
([look](http://stackoverflow.com/questions/17084566/put-stars-on-ggplot-barplots-and-boxplots-to-indicate-the-level-of-significanc) [at](http://stackoverflow.com/questions/14958159/indicating-the-statistically-significant-difference-in-bar-graph-using-r) [all](http://stackoverflow.com/questions/29263046/how-to-draw-the-boxplot-with-significant-level) [those](http://stackoverflow.com/questions/29186435/showing-significance-relationships-in-a-ggplot2-bar-graph) [questions](https://groups.google.com/forum/#!topic/ggplot2/ntVlMqTc6PI)). 
The usual answer is along the lines of just manually adding lines and annotation to the plot.

But I believe that a fundamental strength of ggplot is that it allows one to quickly make advanced plots by combining layers of visualization, which can encapsulate complex statistical methods (`geom_smooth`, `geom_contour` etc.).

So I created this package which provides a single layer `geom_signif` which can calculate the significance of a difference between groups and add the annotation to the plot in a single line.

# How to use it?

First load poth packages

```{r}
library(ggplot2)
library(ggsignif)
```

Second step: plot your data

```{r fig.width = 6, fig.height = 4.8}
ggplot(iris, aes(x=Species, y=Sepal.Length)) + 
  geom_boxplot() +
  geom_signif(comparisons = list(c("versicolor", "virginica")), 
              map_signif_level=TRUE)
```

That's it, it is really simple!

## Advanced options

Sometimes one might need more advanced control over the display. Following the patterns of other ggplot layers, 
one just provides the data and necessary aesthetics and the layer takes care of the rest.

```{r fig.width = 6, fig.height = 4.8}
dat <- data.frame(Group = c("S1", "S1", "S2", "S2"),
                  Sub   = c("A", "B", "A", "B"),
                  Value = c(3,5,7,8))  

ggplot(dat, aes(Group, Value)) +
  geom_bar(aes(fill = Sub), stat="identity", position="dodge", width=.5) +
  geom_signif(stat="identity",
              data=data.frame(x=c(0.875, 1.875), xend=c(1.125, 2.125),
                              y=c(5.8, 8.5), annotation=c("**", "NS")),
              aes(x=x,xend=xend, y=y, yend=y, annotation=annotation)) +
  geom_signif(comparisons=list(c("S1", "S2")), annotations="***",
              y_position = 9.3, tip_length = 0, vjust=0.4) +
  scale_fill_manual(values = c("grey80", "grey20"))
    
```

For more detailed documentation of the available parameters see the man page for the geom_signif function (`> ?geom_signif`).

# Bugs, Comments or Questions?

If you have any problems with the package, just file an issue at https://github.com/Artjom-Metro/ggsignif.
















