---
title: "ggsignif intro"
author: "Constantin Ahlmann-Eltze"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{ggsignif intro}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This package provides an extension for the popular ggplot2 package.

Often people are looking for a way to quickly annotate if the difference between 2 groups in a plot is
significantly different 
([look](http://stackoverflow.com/questions/17084566/put-stars-on-ggplot-barplots-and-boxplots-to-indicate-the-level-of-significanc) [at](http://stackoverflow.com/questions/14958159/indicating-the-statistically-significant-difference-in-bar-graph-using-r) [all](http://stackoverflow.com/questions/29263046/how-to-draw-the-boxplot-with-significant-level) [those](http://stackoverflow.com/questions/29186435/showing-significance-relationships-in-a-ggplot2-bar-graph) [questions](https://groups.google.com/forum/#!topic/ggplot2/ntVlMqTc6PI)). 
The usual answer is along the lines of just manually adding lines and annotation to the plot.

But I believe that a fundamental strength of ggplot is that it allows one to quickly make advanced plots by combining layers of visualization, which can encapsulate complex statistical methods (`geom_smooth`, `geom_contour` etc.).

So I created this package which provides a single layer `geom_signif` which can calculate the significance of a difference between groups and add the annotation to the plot in a single line.

# How to use it?

First load poth packages

```{r}
library(ggplot2)
library(ggsignif)
```

Second step: plot your data

```{r fig.width = 6, fig.height = 4.8}
ggplot(iris, aes(x=Species, y=Sepal.Length)) + 
  geom_boxplot() +
  geom_signif(comparisons = list(c("versicolor", "virginica")), 
              map_signif_level=TRUE)
```

That's it, it is really simple!

## Advanced options

Sometimes one might need more advanced control over the display. To specify exactly where
the bracket is drawn use the `y_position`, `xmin` and `xmax` parameters combined with
a custom `annotations`. This is always necessary if `geom_signif` is combined with
another layer that uses `position="dodge"`, because it changes the location of the 
visual elements without updating the data.

```{r fig.width = 6, fig.height = 4.8}
dat <- data.frame(Group = c("S1", "S1", "S2", "S2"),
                  Sub   = c("A", "B", "A", "B"),
                  Value = c(3,5,7,8))  

ggplot(dat, aes(Group, Value)) +
  geom_bar(aes(fill = Sub), stat="identity", position="dodge", width=.5) +
  geom_signif(y_position=c(5.3, 8.3), xmin=c(0.8, 1.8), xmax=c(1.2, 2.2),
              annotation=c("**", "NS"), tip_length=0) +
  geom_signif(comparisons=list(c("S1", "S2")),
              y_position = 9.3, tip_length = 0, vjust=0.2) +
  scale_fill_manual(values = c("grey80", "grey20"))
    
```

For more detailed documentation of the available parameters see the man page for the geom_signif function (`> ?geom_signif`).

# Bugs, Comments or Questions?

If you have any problems with the package, just file an issue at https://github.com/const-ae/ggsignif.
















