---
title: "ggsignif: Displaying Significance Brackets for 'ggplot2'"
tags:
  - R
  - ggplot2
  - ggplot2-extension
authors:
  - name: Constantin Ahlmann-Eltze
    orcid: 0000-0002-3762-068X
    affiliation: 1
  - name: Indrajeet Patil
    orcid: 0000-0003-1995-6531
    affiliation: 2
affiliations:
  - name: The European Molecular Biology Laboratory, Heidelberg, Germany
  - name: Center for Humans and Machines, Max Planck Institute for Human Development, Berlin, Germany
citation_author: Ahlmann-Eltze & Patil 
date: "`r Sys.Date()`"
year: 2021
bibliography: paper.bib
output: rticles::joss_article
csl: apa.csl
journal: JOSS
link-citations: yes
---

```{r echo=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  dpi = 300,
  warning = FALSE,
  message = FALSE,
  out.width = "100%",
  comment = "#>"
)
```

# Summary

Research hypotheses often concern with differences between two or multiple
groups and (Frequentist and Bayesian) hypothesis testing can provide indices
(*p*-value or Bayes Factor) for evidence for such differences. In the context of
visualizing these group differences, the `ggsignif` package provides a quick way
to annotate the difference between two levels of groups in a plot. These
annotations can signify if the group differences are statistically different. It
provides a single layer `geom_signif` to achieve this. In doing so, it further
extends the fundamental strength of the `ggplot` package [@Wickham2016]: the
ability to quickly make advanced plots encapsulating complex statistical methods
by combining layers of visualization.

# Statement of Need

Often when researchers statistically analyze data, they run a one-way or a
multi-way ANOVA to assess if *any* of the group means differ from each other,
and then follow up these global difference-related analysis with more
fine-grained. *post hoc* multiple comparisons between different levels of the
grouping variables (also called as design factors). The `ggsignif` package
provides a way to graphically display all or a few (depending on the context of
the research hypotheses ) of such comparisons. It is also used by developers of
other R packages as the back-end for graphical displays of pairwise comparisons,
such as `ggpubr` [@Kassambara2020], `ggstatsplot` [@Patil2018], and more. These
packages also highlight how the package can be extended to display results from
any type of pairwise comparisons test, e.g. Bayesian *t*-test, Dunn test, etc.

# Features

The following is a simple example demonstrating how a group difference can be
annotated using `geom_signif` layes from `ggsignif` package.

```{r simpe_comparison}
library(ggplot2)
library(ggsignif)

ggplot(mpg, aes(class, hwy)) +
  geom_boxplot() +
  geom_signif(
    comparisons = list(c("compact", "midsize"), c("minivan", "suv")),
    map_signif_level = TRUE
  ) +
  ylim(NA, 48)
```

For more advanced examples, the readers are encouraged to read the package
website: <https://const-ae.github.io/ggsignif/>.

# Licensing and Availability

`ggsignif` is licensed under the GNU General Public License (v3.0), with all
source code stored at [GitHub](https://github.com/const-ae/ggsignif), and with a
corresponding issue tracker for bug reporting and feature enhancements. In the
spirit of honest and open science, we encourage requests/tips for fixes, feature
updates, as well as general questions and concerns via direct interaction with
contributors and developers, by [filing an issue](https://github.com/const-ae/ggsignif/issues). See the
[*Contribution Guidelines*](https://github.com/const-ae/ggsignif/blob/master/CODE_OF_CONDUCT.md) for this package.

# Acknowledgements

We would like to thanks the users of `ggsignif` package for reporting bugs and
for providing valuable feedback.

# References
